Effect of multiple reflection of the sky signal off the HERA element on the measurements of 21cm power spectrum

### 2015-12-10 DishReflectometry/Paper1_v0.tex
Sorted out some of the references and sorting more.

Since it was first proposed in \citet{shaver_et_al1999}, measuring 21~cm
emission from neutral hydrogen in our early universe has gained attention as a
powerful probe of both cosmology and astrophysics.  While the science case for
21~cm cosmology, particularly during the Epoch of Reionization, is well
established (see, e.g.,
\citealt{furlanetto_et_al2006,morales_wyithe2010,furlanetto_loeb2014,pritchard_loeb2014}),
the technical path toward measuring this signal has been more problematic.  The
weakness of this hyperfine line keeps the 21~cm signal below opacity throughout
cosmological history, but it also creates sensitivity and calibration
challenges that have yet to be fully solved.  With noise temperatures dominated
by sky noise \citep{XXX} and foregrounds four to five orders of magnitude
brighter than the signal \citep{XXX}, 
sky-averaged 21~cm monopole experiments such as
(EDGES; \citealt{XXX}),
(BIGHORNS; \citealt{XXX}),
(SARAS; \citealt{patra_et_al2014}),
(SCIHI; \citealt{voytek_et_al2014}),
(HyPerion; \citealt{presley_et_al2015})
% XXX others?
and 21~cm reionization power spectrum experiments such as
the LOw Frequency ARray (LOFAR; \citealt{XXX}),
the Murchison Widefield Array (MWA; \citealt{XXX}),
the Giant Metre-wave Radio Telescop (GMRT; \citealt{XXX}),
the Donald C. Backer Precision Array to Probe the Epoch of Reionization (PAPER; \citealt{parsons_et_al2010}),
the Hydrogen Epoch of Reionization Array (HERA; \citealt{XXX}),
and the future Square Kilometre Array (SKA; \citealt{XXX})
must
furnish both collecting area and foreground suppression at levels significantly
beyond anything previously achieved in radio telescopes operating below 1 GHz.

@@

\bibliographystyle{apj}
\bibliography{biblio.bib}
%\begin{thebibliography}{}
%
%\bibitem[Parsons \& Backer(2009)]{ParsonsBacker2009}
%Parsons, A., \& Backer, D. 2009, \apj, 138, 219
%\bibitem[Parsons et al.(2012)]{Parsons2012}
%Parsons, A., \& Pober, Jonathan C., \& Aguirre, James E., \& Carilli, Christopher L., \& Jacobs, Daniel C., \& Moore, David F. 2012, \apj 756, 165
%\end{thebibliography}{}

\end{document}

%\begin{eqnarray}
%V e^{i\phi}(\nu) & = & \int |A_{f}|^{2}|V_{sky}|^{2}|exp({2\pi i \nu \vec{b}.\hat{s} \over c} ) d\Omega \nonumber\\
%&& +  \int |A_{f}|^{2}|V_{sky}|^{2} |(1-\Gamma_{f})|^{2}|\Gamma_{f}|^{2}|\Gamma_{d}|^{2} exp({2\pi i \nu \vec{b}.\hat{s} \over c} ) d\Omega \nonumber\\
%&& + \int |A_{f}|^{2}|V_{sky}|^{2}| 2 \Re \left ((1-\Gamma_{f})\Gamma_{f}\Gamma_{d} e^{i\Phi} \right)exp({2\pi i \nu \vec{b}.\hat{s} \over c} ) d\Omega
%\label{eq8}		        
%\end{eqnarray}

%\subsection{Effect of first reflection on the delay spectrum}
%We define $B(\vec \theta, \nu) =  A^{2}(\vec \theta, \nu) $ as the cross power pattern of the interferometer and $\Sigma_{rr}(\nu), \Sigma_{dr}(\nu)$ are the correlation coefficient between the two reflected signals in each antenna and the direct signal of one antenna with the reflected signal from the other antenna in the uv plane i.e,

%\begin{equation}
%\Sigma_{rr}(\nu) =  \left [ |(1-\Gamma_{f})|^{2}|\Gamma_{f}|^{2}|\Gamma_{d}|^{2} \right ]
%\end{equation}

%\begin{equation}
%\Sigma_{dr}(\nu) = \left [ 2 \Re \left ((1-\Gamma_{f})\Gamma_{f}\Gamma_{d} e^{i\Phi} \right) \right]
%\end{equation}

%and $\Delta \tau$ is the additional delay each reflected component suffers in addition to the intrinsic geometric delay 
%$\tau_{g}$. Therefore, $\Sigma(\vec \theta, \nu) = B(\vec \theta, \nu) \left [ 1+\Sigma_{rr} +\Sigma_{dr} \right]$

%As given in equation \ref{eq3}, the Fourier transform of this visibility spectrum along the frequency axis results in the delay spectrum. Hence, the all sky integrated delay spectrum could be written as, 
%\begin{eqnarray}
%\mathcal{F} \left [V e^{i\phi}\right] & = & \int \left [\int B I_{sky}exp({2\pi i \nu \vec{b}.\hat{s} \over c} ) d\Omega \right ] exp\left[ -2 \pi i\nu \tau \right] d\nu \nonumber\\
%&& + \int \left [  \int B I_{sky} \Sigma_{rr} exp({2\pi i \nu \vec{b}.\hat{s} \over c} ) d\Omega \right] exp\left[ -2 \pi i\nu \tau \right] d\nu  \nonumber\\
%&& +\int \left [ \int B I_{sky} \Sigma_{dr} exp({2\pi i \nu \vec{b}.\hat{s} \over c} ) d\Omega \right ] exp\left[ -2 \pi i\nu \tau \right] d\nu \nonumber\\	
%&& + \int \left [  \int |A_{f}|^{2}|V_{sky}|^{2} |(1-\Gamma_{f})|^{2}|\Gamma_{f}|^{2}|\Gamma_{d}|^{2} exp({2\pi i \nu \vec{b}.\hat{s} \over c} ) d\Omega \right] exp\left[ -2 \pi i\nu \tau \right] d\nu  \nonumber\\
%&& +\int \left [ \int |A_{f}|^{2}|V_{sky}|^{2} 2 \Re \left ((1-\Gamma_{f})\Gamma_{f}\Gamma_{d} e^{i\Phi} \right)exp({2\pi i \nu \vec{b}.\hat{s} \over c} ) d\Omega \right ] exp\left[ -2 \pi i\nu \tau \right] d\nu \nonumber\\			
%			& = & \int \left [\int B I_{sky} exp({2\pi i \nu \tau_{g}} ) dl dm \right ] exp\left[ -2 \pi i\nu \tau \right] d\nu \nonumber\\
%&& + \int \left [  \int B I_{sky} \Sigma_{rr} exp({2\pi i \nu \tau_{g}} ) dl dm \right] exp\left[ -2 \pi i\nu \tau \right] d\nu  \nonumber\\
%&& +\int \left [ \int B I_{sky} \Sigma_{dr} exp({2\pi i \nu \tau_{g}} ) dl dm \right ] exp\left[ -2 \pi i\nu \tau \right] d\nu \nonumber\\
%\label{eq9}
%\end{eqnarray}
%
%\begin{eqnarray}			
%\mathcal{F} \left [V e^{i\phi}\right] & = & \left [ B(\tau)\ast I_{sky}(\tau) \right ]\ast \delta(\tau+\tau_{g}) \nonumber\\
%		&& +  \left [ B(\tau)\ast I_{sky}(\tau)* \Sigma_{rr}( \tau) \right ]\ast \delta(\tau+\tau_{g}) \nonumber\\
%		&& +  \left [B(\tau)\ast I_{sky}(\tau)* \Sigma_{dr}( \tau) \right ]\ast \delta(\tau+\tau_{g}+ \Delta \tau)\nonumber\\
%\label{eq10}
%\end{eqnarray}

 %In words, the Fourier transform of the visibility contributed by any two voltage components from two antennas with no mutual delay is centred at a delay $\tau = \tau_{g}$ in the delay spectrum whereas any two voltage components from two antennas components having a mutual delay of $\Delta \tau$ will be centred at $\tau_{g} +\Delta \tau$. The correlation between the reflected signal  from the feed and subsequently from the dish with the direct signal thus extends the foreground response to delays beyond the maximum geometric delay for a given baseline and contaminates the delay mode where 21~cm delay spectrum could potentially be detected. Also, any reflections arriving at the feed at any non-zero  value of the delay $\Delta \tau$ which could be the result of reflections from the feed structures would generate non zero delay response at those delays.

>>>>

Since it was first proposed in \citep{Shaver_et_al1999} measuring 21~cm
emission from neutral hydrogen in our early universe has gained attention as a
powerful probe of both cosmology and astrophysics.  While the science case for
21~cm cosmology, particularly during the Epoch of Reionization, is well
established (see, e.g.,
\citep{furlanetto_et_al2006,morales_wyithe2010,pritchard_loeb2012}),
the technical path toward measuring this signal has been more problematic.  The
weakness of this hyperfine line keeps the 21~cm signal below opacity throughout
cosmological history, but it also creates sensitivity and calibration
challenges that have yet to be fully solved.  With noise temperatures dominated
by sky noise \citep{XXX} and foregrounds four to five orders of magnitude
brighter than the signal \citep{XXX}, 
sky-averaged 21~cm monopole experiments such as
(EDGES; \citealt{XXX}),
(BIGHORNS; \citealt{XXX}),
(SARAS; \citealt{patra_et_al2014}),
(SCIHI; \citealt{voytek_et_al2014}),
(HyPerion; \citealt{presley_et_al2015})
% XXX others?
and 21~cm reionization power spectrum experiments such as
the LOw Frequency ARray (LOFAR; \citealt{XXX}),
the Murchison Widefield Array (MWA; \citealt{XXX}),
the Giant Metre-wave Radio Telescop (GMRT; \citealt{XXX}),
the Donald C. Backer Precision Array to Probe the Epoch of Reionization (PAPER; \citealt{parsons_et_al2010}),
the Hydrogen Epoch of Reionization Array (HERA; \citealt{XXX}),
and the future Square Kilometre Array (SKA; \citealt{XXX})
must
furnish both collecting area and foreground suppression at levels significantly
beyond anything previously achieved in radio telescopes operating below 1 GHz.

@@

\bibliographystyle{apj}
\bibliography{biblio.bib}
\end{document}
